A Plot is Worth a Thousand Tests: Assessing Residual Diagnostics with the Lineup Protocol

### 2023-04-03 paper.Rmd
rearranged main paper and appendix into separate files again

$$E = \frac{1}{2}\left(log\frac{|diag(\boldsymbol{R}_a\boldsymbol{V}\boldsymbol{R}_a')|}{|diag(\boldsymbol{R}_a)|} - n + tr(diag(\boldsymbol{R}_a\boldsymbol{V}\boldsymbol{R}_a')^{-1}diag(\boldsymbol{R}_a))\right)$$
\noindent where $\boldsymbol{V}$ is the actual covariance matrix of the error term.

Derivations for these equations are provided in the Appendix.

@@

To account for the fact that our simulation method for these lineups is not the Rorschach procedure, we use the method suggested in @vanderplas2021statistical for typical lineups containing a data plot to estimate $\alpha$. 
We have included a sensitivity analysis in the Appendix to examine the impact of the variance of the $\alpha$ estimate on our findings.

@@

\appendix

>>>>

$$E = \frac{1}{2}\left(log\frac{|diag(\boldsymbol{R}_a\boldsymbol{V}\boldsymbol{R}_a')|}{|diag(\boldsymbol{R}_a)|} - n + tr(diag(\boldsymbol{R}_a\boldsymbol{V}\boldsymbol{R}_a')^{-1}diag(\boldsymbol{R}_a))\right)$$
\noindent where $\boldsymbol{V}$ is the actual covariance matrix of the error term. (Derivations for these equations are provided in the Appendix.)

@@

To account for the fact that our simulation method for these lineups is not the Rorschach procedure, we use the method suggested in @vanderplas2021statistical for typical lineups containing a data plot to estimate $\alpha$. 
(We have included a sensitivity analysis in the Appendix to examine the impact of the variance of the $\alpha$ estimate on our findings.)

@@

### 2023-04-03 paper.tex
rearranged main paper and appendix into separate files again

\[E = \frac{1}{2}\left(log\frac{|diag(\boldsymbol{R}_a\boldsymbol{V}\boldsymbol{R}_a')|}{|diag(\boldsymbol{R}_a)|} - n + tr(diag(\boldsymbol{R}_a\boldsymbol{V}\boldsymbol{R}_a')^{-1}diag(\boldsymbol{R}_a))\right)\]
\noindent where \(\boldsymbol{V}\) is the actual covariance matrix of
the error term.

Derivations for these equations are provided in the Appendix.

@@

To account for the fact that our simulation method for these lineups is
not the Rorschach procedure, we use the method suggested in
\citet{vanderplas2021statistical} for typical lineups containing a data
plot to estimate \(\alpha\). We have included a sensitivity analysis in
the Appendix to examine the impact of the variance of the \(\alpha\)
estimate on our findings.

>>>>

\[E = \frac{1}{2}\left(log\frac{|diag(\boldsymbol{R}_a\boldsymbol{V}\boldsymbol{R}_a')|}{|diag(\boldsymbol{R}_a)|} - n + tr(diag(\boldsymbol{R}_a\boldsymbol{V}\boldsymbol{R}_a')^{-1}diag(\boldsymbol{R}_a))\right)\]
\noindent where \(\boldsymbol{V}\) is the actual covariance matrix of
the error term. (Derivations for these equations are provided in the
Appendix.)

@@

To account for the fact that our simulation method for these lineups is
not the Rorschach procedure, we use the method suggested in
\citet{vanderplas2021statistical} for typical lineups containing a data
plot to estimate \(\alpha\). (We have included a sensitivity analysis in
the Appendix to examine the impact of the variance of the \(\alpha\)
estimate on our findings.)
